Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd
Close #107

```{r t1, results='asis', fig.cap="Summary of the road segment dataset for Leeds.", message=FALSE}
rj_leeds = readRDS("r_main_leeds.Rds")
# See https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html
# rj_leeds %>%
#   st_drop_geometry() %>%
#   mutate(`width (m)` = width) %>%
#   select(name, highway_type, maxspeed, cycling_potential, `width (m)`, n_lanes) %>%
#   group_by(maxspeed) %>% 
#   # qwraps2::summary_table()
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = .)
t1 = readr::read_csv("input-data/t1.csv")[-1]
t1 = t1 %>% 
  rename("20 mph (32.2 kmph) or less" = "20 mph or less", "30 mph (48.3 kmph)" = "30 mph", "40+ mph (64.4 kmph)" = "40+ mph")
n = c(
  "",
  "4777",
  "19241",
  "3105",
  "27123"
)
names(n) = names(t1)
t2 = rbind(n, t1)
names(t2)[1] = ""
# t1
t2 %>% 
  kableExtra::kable(caption = "Summary of the road segment dataset for Leeds.",
    # escape = FALSE,
    booktabs = TRUE,
    # col.names = kableExtra::linebreak(names(t1)),
    format = "latex"
    ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::pack_rows("N. observations", 1, 2) %>% 
  kableExtra::pack_rows("Highway type", 2, 13) %>% 
  kableExtra::pack_rows("Cycling potential", 14, 15) %>%  
  kableExtra::pack_rows("Width (m)", 16, 18) %>% 
  kableExtra::pack_rows("N. lanes", 19, 22)

>>>>

```{r t1, results='asis', message=FALSE}
rj_leeds = readRDS("r_main_leeds.Rds")
# See https://cran.r-project.org/web/packages/qwraps2/vignettes/summary-statistics.html
# rj_leeds %>%
#   st_drop_geometry() %>%
#   mutate(`width (m)` = width) %>%
#   select(name, highway_type, maxspeed, cycling_potential, `width (m)`, n_lanes) %>%
#   group_by(maxspeed) %>% 
#   # qwraps2::summary_table()
#   table1::table1(~ highway_type + cycling_potential + `width (m)` + n_lanes | maxspeed, data = .)
t1 = readr::read_csv("input-data/t1.csv")[-1]
n = c(
  "",
  "4777",
  "19241",
  "3105",
  "27123"
)
names(n) = names(t1)
t2 = rbind(n, t1)
names(t2)[1] = ""
# t1
t2 %>% 
  kableExtra::kable(caption = "Summary of the road segment dataset for Leeds. Units of speed are in miles per hour (mph), with 20, 30 and 40 mph representing 32, 48 and 64 kilometers per hour respectively.",
    # escape = FALSE,
    booktabs = TRUE,
    # col.names = kableExtra::linebreak(names(t1)),
    format = "latex"
    ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::pack_rows("N. observations", 1, 2) %>% 
  kableExtra::pack_rows("Highway type", 2, 13) %>% 
  kableExtra::pack_rows("Cycling potential", 14, 15) %>%  
  kableExtra::pack_rows("Width (m)", 16, 18) %>% 
  kableExtra::pack_rows("N. lanes", 19, 22)

### 2020-06-22 article.tex
Close #107

\caption{\label{tab:t1}Summary of the road segment dataset for Leeds.}
\centering
\begin{tabular}[t]{lllll}
\toprule
 & 20 mph (32.2 kmph) or less & 30 mph (48.3 kmph) & 40+ mph (64.4 kmph) & Overall\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{N. observations}}\\
\hspace{1em} & 4777 & 19241 & 3105 & 27123\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Highway type}}\\
\hspace{1em}\hspace{1em}bridleway & 53 (1.1\%) & 0 (0\%) & 0 (0\%) & 53 (0.2\%)\\
\hspace{1em}cycleway & 1214 (25.4\%) & 0 (0\%) & 0 (0\%) & 1214 (4.5\%)\\
\hspace{1em}footway & 1332 (27.9\%) & 0 (0\%) & 0 (0\%) & 1332 (4.9\%)\\
\hspace{1em}other & 187 (3.9\%) & 715 (3.7\%) & 1608 (51.8\%) & 2510 (9.3\%)\\
\hspace{1em}pedestrian/living\_street & 22 (0.5\%) & 0 (0\%) & 0 (0\%) & 22 (0.1\%)\\
\hspace{1em}primary & 14 (0.3\%) & 1432 (7.4\%) & 955 (30.8\%) & 2401 (8.9\%)\\
\hspace{1em}residential & 605 (12.7\%) & 8604 (44.7\%) & 0 (0\%) & 9209 (34.0\%)\\
\hspace{1em}secondary & 28 (0.6\%) & 1408 (7.3\%) & 176 (5.7\%) & 1612 (5.9\%)\\
\hspace{1em}service & 1018 (21.3\%) & 7 (0.0\%) & 0 (0\%) & 1025 (3.8\%)\\
\hspace{1em}tertiary & 170 (3.6\%) & 5206 (27.1\%) & 290 (9.3\%) & 5666 (20.9\%)\\
\hspace{1em}unclassified & 134 (2.8\%) & 1869 (9.7\%) & 75 (2.4\%) & 2078 (7.7\%)\\
\hspace{1em}bus\_guideway & 0 (0\%) & 0 (0\%) & 1 (0.0\%) & 1 (0.0\%)\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Cycling potential}}\\
\hspace{1em}Mean (SD) & 39.0 (67.8) & 36.9 (66.7) & 40.7 (55.1) & 37.7 (65.7)\\
\hspace{1em}Median [Min, Max] & 14.0 [1.00, 810] & 15.0 [1.00, 810] & 24.0 [1.00, 519] & 16.0 [1.00, 810]\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Width (m)}}\\
\hspace{1em}Mean (SD) & 6.62 (2.71) & 7.34 (2.28) & 8.84 (2.36) & 7.41 (2.42)\\
\hspace{1em}Median [Min, Max] & 7.00 [1.00, 21.0] & 7.00 [1.00, 24.0] & 9.00 [2.00, 21.0] & 7.00 [1.00, 24.0]\\
\hspace{1em}Missing & 1688 (35.3\%) & 1225 (6.4\%) & 447 (14.4\%) & 3360 (12.4\%)\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{N. lanes}}\\
\hspace{1em}1 & 3840 (80.4\%) & 1555 (8.1\%) & 406 (13.1\%) & 5801 (21.4\%)\\
\hspace{1em}2 & 937 (19.6\%) & 16979 (88.2\%) & 2266 (73.0\%) & 20182 (74.4\%)\\
\hspace{1em}3 & 0 (0\%) & 490 (2.5\%) & 289 (9.3\%) & 779 (2.9\%)\\
\hspace{1em}4+ & 0 (0\%) & 217 (1.1\%) & 144 (4.6\%) & 361 (1.3\%)\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:t1}Summary of the road segment dataset for Leeds. Units of speed are in miles per hour (mph), with 20, 30 and 40 mph representing 32, 48 and 64 kilometers per hour respectively.}
\centering
\begin{tabular}[t]{lllll}
\toprule
 & 20 mph or less & 30 mph & 40+ mph & Overall\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{N. observations}}\\
\hspace{1em} & 4777 & 19241 & 3105 & 27123\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Highway type}}\\
\hspace{1em}\hspace{1em}bridleway & 53 (1.1\%) & 0 (0\%) & 0 (0\%) & 53 (0.2\%)\\
\hspace{1em}cycleway & 1214 (25.4\%) & 0 (0\%) & 0 (0\%) & 1214 (4.5\%)\\
\hspace{1em}footway & 1332 (27.9\%) & 0 (0\%) & 0 (0\%) & 1332 (4.9\%)\\
\hspace{1em}other & 187 (3.9\%) & 715 (3.7\%) & 1608 (51.8\%) & 2510 (9.3\%)\\
\hspace{1em}pedestrian/living\_street & 22 (0.5\%) & 0 (0\%) & 0 (0\%) & 22 (0.1\%)\\
\hspace{1em}primary & 14 (0.3\%) & 1432 (7.4\%) & 955 (30.8\%) & 2401 (8.9\%)\\
\hspace{1em}residential & 605 (12.7\%) & 8604 (44.7\%) & 0 (0\%) & 9209 (34.0\%)\\
\hspace{1em}secondary & 28 (0.6\%) & 1408 (7.3\%) & 176 (5.7\%) & 1612 (5.9\%)\\
\hspace{1em}service & 1018 (21.3\%) & 7 (0.0\%) & 0 (0\%) & 1025 (3.8\%)\\
\hspace{1em}tertiary & 170 (3.6\%) & 5206 (27.1\%) & 290 (9.3\%) & 5666 (20.9\%)\\
\hspace{1em}unclassified & 134 (2.8\%) & 1869 (9.7\%) & 75 (2.4\%) & 2078 (7.7\%)\\
\hspace{1em}bus\_guideway & 0 (0\%) & 0 (0\%) & 1 (0.0\%) & 1 (0.0\%)\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Cycling potential}}\\
\hspace{1em}Mean (SD) & 39.0 (67.8) & 36.9 (66.7) & 40.7 (55.1) & 37.7 (65.7)\\
\hspace{1em}Median [Min, Max] & 14.0 [1.00, 810] & 15.0 [1.00, 810] & 24.0 [1.00, 519] & 16.0 [1.00, 810]\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Width (m)}}\\
\hspace{1em}Mean (SD) & 6.62 (2.71) & 7.34 (2.28) & 8.84 (2.36) & 7.41 (2.42)\\
\hspace{1em}Median [Min, Max] & 7.00 [1.00, 21.0] & 7.00 [1.00, 24.0] & 9.00 [2.00, 21.0] & 7.00 [1.00, 24.0]\\
\hspace{1em}Missing & 1688 (35.3\%) & 1225 (6.4\%) & 447 (14.4\%) & 3360 (12.4\%)\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{N. lanes}}\\
\hspace{1em}1 & 3840 (80.4\%) & 1555 (8.1\%) & 406 (13.1\%) & 5801 (21.4\%)\\
\hspace{1em}2 & 937 (19.6\%) & 16979 (88.2\%) & 2266 (73.0\%) & 20182 (74.4\%)\\
\hspace{1em}3 & 0 (0\%) & 490 (2.5\%) & 289 (9.3\%) & 779 (2.9\%)\\
\hspace{1em}4+ & 0 (0\%) & 217 (1.1\%) & 144 (4.6\%) & 361 (1.3\%)\\
\bottomrule
\end{tabular}
\end{table}
